% =============================================================================
% FILE NAME : 00_introduction.tex
% DEPARTMENT: University of Tuebingen
% AUTOR     : Tom Schammo
% =============================================================================
% CONTENT   : Include for chapter "Introduction"
% =============================================================================

Rust \cite{rustlang} is a somewhat new language, with its very first release in early 2012.
But the 1.0 alpha release was not until early 2015 with the full 1.0 release following a few
months later in May of the same year \cite{rust_releases}.
C, as a comparison has been used as early as the 1970s.\\
But Rust has been gaining in popularity \cite{rust_popularity} over the last few years, however due to its relatively 'young' age,
there still are huge gaps when it comes to software support and available libraries.
Embedded systems is an area where Rust has the potential to be very useful, as it is both very performant and memory safe.
This makes it a potential alternative to C or C++, especially for high-stakes, high-performance, real-time applications.
However, that gap is very noticeable when it comes to embedded devices.\\
Additionally, as machine learning technologies improve and are integrated into IoT and smart devices,
the use cases for hardware-accelerated devices are ever-growing.
As voice-controlled devices, specifically voice assistants (VAs) have become almost omnipresent,
with Siri being shipped with every Apple smartphone, tablet, and laptop,
Google Assistant being installed on every Android phone (except for a few custom ROMs that remove Google software) and Cortana being integrated
into every new Windows operating system, users become increasingly used to these technologies.
The adoption of voice-controlled devices can also be observed in private homes with standalone devices
like the Amazon Echo to control appliances and a variety of IoT gadgets.
However, in the IoT space, security is more often than not, not even an afterthought.
This is mostly a result of software bugs that could be avoided by enforcing memory safety.
In my thesis I will improve upon the Rust ecosystem by extending the work of Raphael Vogelgsang \cite{rust_pulp}
and implementing support for the UltraTrail \cite{ultratrail} AI accelerator.
\\\\
This thesis is structured as follows:
Chapter~\ref{cha:fundamentals} provides a fundamental overview of RISC-V, 'Embedded AI', (embedded) Rust, and microphone technology.
It also briefly introduces the microphones that have been used to evaluate the functionality of the UltraTrail and microphone drivers.\\
Chapter~\ref{cha:related_work} covers previous work on the PULPissimo \cite{pulpissimo} and goes a bit into the UltraTrail architecture.
Finally, it covers the state of keyword spotting in the industry.
It goes briefly into its use cases and then covers one of them a little more in-depth.
The concept of the thesis is covered in Chapter~\ref{cha:concept}.
That chapter briefly introduces what I'm trying to do in my thesis.
It also presents the experiments used to evaluate the UltraTrail and microphone drivers.
Chapter~\ref{cha:results_and_discussion} starts with a discussion of the implementation
of the UltraTrail driver as well as the PDM and $I^2S$ microphones.
This is followed by a presentation of the driver functionality tests and a brief discussion of the results.
Finally, Chapter~\ref{cha:conclusion_and_future_work} concludes this thesis with a summary and discusses any shortcomings.
It also includes a brief discussion of possible future work.
